\Large \bf \projtitle

### 2015-05-08 doc/paper/paper.tex
finish results description

\begin{figure}[h]
% TODO: heatmap here
\caption{Average page load time over P2P for seeders vs leechers}
\end{figure}

\subsubsection{\zbf vs HTTP}
As seen in fig 1, the performance of \zbf depended on the seeder-to-leecher ratio.
In general, the lowest latency in load time was achieved when the seeder-to-leecher
ratio was highest. However, the system performed well in any condition with many
seeder peers, reflecting the performance benefits provided by chunking of resources
and parallelization of sending chunks. The system performed worst when there were many
leechers and only a few seeders.

% TODO: figure out ratio of seeders to leechers
Our next empirical analysis was to keep the ratio of seeders to leechers constant at X,
and compare the page load times for a throttled HTTP server vs \zbf as we increase the
number of users attempting to concurrently load the page.

\begin{figure}[h]
% TODO: other plot here
% TODO: figure out ratio of seeders to leechers
\caption{Average page load time over P2P compared to HTTP on throttled server assuming
constant ratio of X seeders per leecher}
\end{figure}

>>>>

\begin{figure}[heatmap.pdf]
% TODO: heatmap here
\caption{Average page load time over P2P for seeders vs leechers}
\end{figure}

As seen in figure 1, the performance of \zbf depended on the seeder-to-leecher ratio.
In general, the lowest latency in load time was achieved when the seeder-to-leecher
ratio was highest. However, the system performed well in any condition with many
seeder peers, reflecting the performance benefits provided by chunking of resources
and parallelization of sending chunks. The system performed worst when there were many
leechers and only a few seeders.

\subsubsection{\zbf vs HTTP}
% TODO: figure out ratio of seeders to leechers
Our next empirical analysis was to keep the ratio of seeders to leechers constant at X,
and compare the page load times for a throttled HTTP server vs \zbf as we increase the
number of users attempting to concurrently load the page.

\begin{figure}[lineplot.pdf]
% TODO: other plot here
% TODO: figure out ratio of seeders to leechers
\caption{Average page load time over P2P compared to HTTP on throttled server assuming
constant ratio of X seeders per leecher}
\end{figure}

As seen in figure 2, \zbf performed well in comparison to loading content over HTTP.
While both experienced increases in content delivery latency with increasing numbers
of peers requesting content, in general \zbf had lower latency than HTTP. Note
that our simulated "reddit effect" implies hundreds of thousands of other
simultaneous connection; however, since we are simulating the effect, these
imaginary peers cannot distribute content to new peers. So, \zbf could potentially
provide an even greater latency drop with more active seeding peers, which would
be the case in a real-world scenario.
